\cvsection{Languages}
\cvtag{C}
\cvtag{Python}
\cvtag{Java}
\cvtag{Typescript}
\cvtag{Lua}

\cvsection{Technologies}
\cvtag{Amazon Web Services}
\cvtag{Firebase}
\cvtag{Nix}
\cvtag{Linux}
\cvtag{ReactJS}
\cvtag{VueJS}
\cvtag{Angular 7}
\cvtag{NodeJS}
\cvtag{HTML5}
\cvtag{Cypress}
\cvtag{Locust}

\cvsection{Projects}

\cvproject{SwayFX}{October 2021 - Present}
\begin{itemize}
    \item The Sway Linux compositor lacked visual effects, making it unpleasing to use.
    \item Lead the design and implementation of a new renderer, introducing visual flair while maintaining Sway’s performance, configuration, and developer ergonomics.
    \item Leveraged C and OpenGL to implement custom window animations, shadows, background blur, and rounded corners while integrating user feedback and troubleshooting issues.
    \item Delivered SwayFX, an enhanced fork of Sway with visual aesthetics. The fork has amassed over 1900 stars on GitHub and an estimateed 10,000 users across 14 Linux distributions.
\end{itemize}

\divider

\cvproject{SceneFX}{July 2023 - Present}
\begin{itemize}
    \item Few Linux compositors have visual effects, due to a feature gap in the wlroots rendering library, although SwayFX had a renderer capable of visual effects.
    \item Lead the design and implementation of extracting and refactoring SwayFX’s renderer into a general-purpose, compositor-agnostic rendering library.
    \item Created SceneFX, a drop-in renderer capable of rendering with advanced visuals across the wlroots ecosystem that has been adopted by at least 4 wayland compositors that total over 3000 stars on GitHub.
\end{itemize}

\cvsection{Education}
\cveducation{Bachelor of Engineering, Computer}{University of Guelph}{2017 -- 2022}

